Introducing the \NAME Framework\\ for Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-06 paper.tex
made title casing more consistent
augmenting the boringness-factor ;-)

\title{
Introducing the \NAME framework\\
for efficient Intrusion Detection\\
in the Internet of Things
}

@@

The promise of the Internet of Things (IoT) is exciting: my smart car will
notify the my smart home \cite{aldrich2003smart} that I will be late. It now
can turn up the heat later, thus lowering my energy bills and adding to a
greener world. Wonderful, I'm in. But what if the energy company can do the
same? What if they are able to turn up the heat while I'm gone, making my home
nice and cosy but also cranking up my bill and their profit. No thank you, let
me out.

Along with all the wonderful possibilities, the IoT clearly holds a significant
threat: by opening our homes and lives to all these interconnected devices, we
also open them to everyone who is able to break these new, virtual locks, often
without leaving a trace.

@@

In classic networks, firewalls protect the outer perimeter of the network,
filtering unwanted packets. But attacks on flaws in services can pass
unnoticed. This is where intrusion detection (ID) steps in: an ID probe
monitors all traffic that passes through the firewall, looking for patterns and
optionally alerting the firewall if a malicious pattern is detected.

@@

In mobile ad hoc networks (MANET), which make up an important part of the IoT,
it is not possible to have this single point in the network that can oversee
all traffic \cite{mishra2004intrusion}. If the outer security perimeter
diminishes, every device has to implement its own lines of defence.
Localisation of the IDS requires resources, and resources are another important
factor to consider: IoT devices typically have limited batteries, little
processing power and memory is restricted to the bare minimum.

@@

The first contribution of this paper is a framework that enables the formal
description of ID algorithms on a functional level. An automated code
generation process produces corresponding source code, for a given platform and
configuration. The way, the framework addresses the heterogeneous nature of
both the IoT as a hardware and software platform, and that of the different ID
algorithms.

>>>>

\title{
Introducing the \NAME Framework\\
for Efficient Intrusion Detection\\
in the Internet of Things
}

@@

Along with its potential, the IoT also presents a significant threat: by
opening our smart homes \cite{aldrich2003smart} and personal data to all these
interconnected devices, we also open them to everyone who is able to break
these new, virtual locks, often without leaving a trace.

@@

In classic networks, firewalls focus on the outer perimeter of the network,
filtering unwanted packets and protecting the entire internal network. But
attacks on flaws in services can pass unnoticed. This is where intrusion
detection (ID) steps in: an ID probe monitors all traffic that passes through
the firewall, looking for patterns and optionally alerting the firewall if a
malicious pattern is detected \cite{denning1987intrusion}.

@@

In mobile ad hoc networks (MANET), which make up an important part of the IoT,
it is not possible to have this single point in the network that can oversee
all traffic \cite{zhang2000intrusion, mishra2004intrusion}. If the outer
security perimeter diminishes, every device has to implement its own lines of
defence. Making the IDS a local service on each device requires resources,
which are another important constraint: IoT devices typically have limited
batteries, little processing power and memory is restricted to the bare minimum.

@@

The first contribution of this paper is a framework that enables the formal
description of ID algorithms on a functional level. An automated code
generation process produces corresponding source code, for a given platform and
configuration. This way, the framework addresses the heterogeneous nature of
both the IoT, as a hardware and software platform, and ID algorithms.
